---
title: "Coseq"
output:
  pdf_document: default
  html_notebook: default
---

Code used to run the Co-expression analysis on the RNAseq data

Manual on coseq on:

https://bioconductor.org/packages/devel/bioc/manuals/coseq/man/coseq.pdf


<span style="color:red">Testing Coseq functionalities on Alberts control plants </span>

##TEST 
This has to be ran from R > 3.4.0

First upload the data

```{r}

#source("https://bioconductor.org/biocLite.R")
#biocLite("coseq")

library(coseq)

matrix <- read.delim("/home/DB2/RNAseq_V2/COUNTS/COSEQ/AC.counts", header = F, row.names = 1)
conds <- rep(c("6h", "24h", "48h", "5d", "8d", "45d", "54d"), each=3)
conds <- rep(c("A", "B", "C", "D", "E", "F", "G"), each=3)

coseqo <- coseqRun(y=matrix, K=9:20, conds = conds,  iter=5, transformation="arcsin")

summary(coseqo)
```

```{r}

plot(coseqo, order=T, conds=conds , average_over_conds=T)

```





Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).


